\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\title{\textbf{Life Is Beautiful: Story of 8 friends}}
\author{\textbf{Riyad-E-Al Muhafiz} }
\date{\today}



\begin{document}

\begin{titlepage}
\maketitle
\thispagestyle{empty} 
\end{titlepage}


\noindent Life is the most precious asset on this planet and must be protected irrespective of its form and appearance. Life can be a truly exciting adventure. But sometimes, there are those days, weeks, months or even years, during which the going gets exceptionally tough. And we can easily pass these hard moments when we have right persons alongside us. There are moments in our life, when we meet someone and we feel as if we have known them all our life. Baltasar Gracian said that \textbf{“\textit{True friendship multiplies the good in life and divides its evils.}”} This story is about 8 very simple people who met in a certain place and the rest is history for them.Let's Begin the story:
All characters of this story are from Pabna city. They got admitted into Pabna Zilla Schiool in 2007. When they are are in class 4 back in 2008, they got to know each of eight people for the first time. But funny thing is they cannot remember how actually they ended up making a group of eight people. Since then they never get separated for a single time. They have millions of stories together. Few of them will be shared in this story. In the classroom there always two bench remain booked for this eight guy. They used to gossip and chatting among them all the time, even if the teacher in the classroom and taking some serious lectures. One of the funny things happened when they were in class six. Once the teacher got very angry seeing that this eight guy is not giving proper concentration on his lecture. He then gave a ban on this eight guy to sit together. He told that if he ever found that they are sitting together again then he would take serious actions against them. But what power on earth can separate these guys! There bonding was so strong that don't had any fear with these kinds of threats or actions. From the very next day they started sitting together. The teacher tried in many ways to separate them and failed every time. Everyone of them were extremely football freak. Coincidentally among eight guy four were Barcelona supporter and another four were supporter of Real Madrid. So after the school ends they went to the field to play El-Classico. Often they had fight on the topic that 'Who is the best, Messi or Ronaldo'. but these were friendly fight and was not too serious. In the school they were very famous friend circle. They had that respect from both their senior and juniors. Reasons behind that, everyone of this circle did not have any bad habits like smoking, teasing girls, fighting with people from outside etc. The most interesting thing is all of these eight guys are actually introvert. They only open up when they are all together. But a situation comes like they had to meet and talk with a random guy then people find them very shy which was very funny.They finished school and college together and currently are in the universities. But their friendship remains the same as before. For the first two years of their university life they get the chance to meet very little as everyone was busy in their academic curriculum. But in 2020 when all universities started online classes for corona virus everyone has gone to their home. As a result they got the chance to meet everyday again. These eight friends are enjoying every moments of their life. When they are at together they forget about tensions, sorrows, pains and enjoy every moments like a happy flying bird. Hopefully their friendship lasts forever and they set the example of 'How true friendship can make life beautiful'. Among eight of them seven guys are doing engineering and one guy has started his own business. Now let's know the name and current situations of each of them.
\textbf{Abrar} is currently pursuing his bachelor from AUST in Mechanical Engineering. He is tall and very matured guy. \textbf{Borshon} is doing Electrical and Electronics Engineering from JUST. Food is love for this guy. One thing that always remain in his head that he needs to eat .\textbf{Mirajul} has started his own business and making moneys all by himself. Also he has a dance academy called 'Shonar Bangla Ma Academy'\textbf{Showmik} and \textbf{Sazzad} Both are studying in Computer Science and Engineering from DIU. They are like Motu-Patlu character. They do every work together and enjoy to be with together. \textbf{Sadi} showing his class in IIT of DU. This guy is extremely talented and become the center of attention everywhere he goes. \textbf{Shoshi} is doing Mechanical Engineering From KUET. He is a habit to talk about football always. Sometimes people get offended by this, because talking the same thing all the time is not very impressive. Finally \textbf{Riyad} is doing Software Engineering in IUT. He plays football very well and playing football is his favourite thing to do. So that was all about the story!



\end{document}
